Supporting Information

### 2016-12-12 portfolio/text/ms.Rmd
Results and supp edits

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort, specializing tends to be
associated with increased revenue (Fig. \ref{fig:within}; Fig. S\ref{fig:fe}).
On average, there is a ~0.5% increase in the year-to-year revenue ratio per 1%
decrease in species diversity, and across strategies, `r g2_dens`% of the
probability density supports a positive relationship between specialization and
revenue. The converse is also usually true --- generalizing tends to be
associated with lower expected revenue after accounting for fishing effort (i.e.
Fig. S\ref{fig:mirror}A and \ref{fig:mirror}B are near mirror images left to
right). This benefit of specializing is only apparent after accounting for
fishing effort. Given that fishing for more species tends to be associated with
increased fishing effort (fishing more days), generalizing tends to be
associated with higher revenue when not standardizing for days finished (Fig.
S-TODO).

After accounting for fishing effort, adjusting (increasing or decreasing) an
individual's fished species diversity within the constraints of a permit set
tends to be associated with greater expected variability or uncertainty in
year-to-year revenue (Fig. \ref{fig:within} strategies above 0; Fig.
S\ref{fig:fe}). This effect was strongest for individuals with a halibut permit
or halibut and sablefish permits. Individuals with these strategies experienced
~2% increase in variability for a 1% change in the year-to-year ratio of species
diversity (Fig. \ref{fig:within}). Levels of fished species diversity above one
for these particular permits are primarily due to bycatch.

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994. This catch share system... TODO. We refit our
models allowing all permit-level effects to vary separately before and after the
introduction of IFQs for strategies involving halibut and sablefish permits. The
introduction of IFQs reduced variability by ~25% (XX--XX 95% CI) for individuals
with only halibut or sablefish permits (Fig. S\ref{fig:ifq}A). Furthermore, for
most strategies, the association changing species diversity with increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\ref{fig:ifq}B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\ref{fig:ifq}B).

>>>>

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort, specializing tends to be
associated with increased revenue (Fig. \ref{fig:within}; Fig. S\ref{fig:fe},
Fig. S\ref{fig:re}). On average, there is a ~0.5% increase in the year-to-year
revenue ratio per 1% decrease in species diversity, and across strategies, `r
g2_dens`% of the probability density supports a positive relationship between
specialization and revenue. The converse is also usually true --- generalizing
tends to be associated with lower expected revenue after accounting for fishing
effort (i.e. Fig. S\ref{fig:mirror}A and \ref{fig:mirror}B are near mirror
images left to right). This benefit of specializing is only apparent after
accounting for fishing effort. Given that fishing for more species tends to be
associated with increased fishing effort (fishing more days), generalizing tends
to be associated with higher revenue when not standardizing for days finished
(Fig. S-TODO).

After accounting for fishing effort, adjusting (increasing or decreasing) an
individual's fished species diversity within the constraints of a permit set
tends to be associated with greater expected variability or uncertainty in
year-to-year revenue (Fig. \ref{fig:within} strategies above 0; Figs.
S\ref{fig:fe}, \ref{fig:re}, \ref{fig:mirror}). This effect was strongest for
individuals with a halibut permit or halibut and sablefish permits. Individuals
with these strategies experienced ~2% increase in variability for a 1% change in
the year-to-year ratio of species diversity (Fig. \ref{fig:within}). Levels of
fished species diversity above one for these particular permits are primarily
due to bycatch.

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994. This catch share system... TODO. We refit our
models allowing all strategy-level effects to vary separately before and after the
introduction of IFQs for strategies involving halibut and sablefish permits. The
introduction of IFQs reduced variability by ~25% (XX--XX 95% CI) for individuals
with only halibut or sablefish permits (Fig. S\ref{fig:ifq}A). Furthermore, for
most strategies, the association changing species diversity with increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\ref{fig:ifq}B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\ref{fig:ifq}B).

### 2016-12-12 portfolio/text/supp.Rnw
Results and supp edits

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.1\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year-to-year for
individual permit holders \emph{within} the `r nstr` most common strategies.
Changing species diversity from year-to-year is associated with higher
variability for individuals within the strategies above the zero line.
Generalizing (A) or specializing (B) is associated with greater expected revenue
to the right of the zero line and lower expected revenue to the left of the zero
line. These effects are estimated holding fishing season length constant from
year-to-year. Dots and line segments represent medians and 50\% credible
intervals of posteriors. }
\label{fig:mirror}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.05\textwidth]{../figs/stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year-to-year for
  individual permit holders \emph{within} the \Sexpr{nstr} most common
  strategies. Changing species diversity from year-to-year is associated with
  higher variability for individuals within the strategies above the zero line.
  Generalizing (A) or specializing (B) is associated with greater expected
  revenue ratios to the right of the zero line and lower expected revenue ratios
  to the left of the zero line. These effects are estimated holding fishing
  season length constant from year-to-year. Dots and line segments represent
  medians and 50\% credible intervals of posteriors. Panel B and Fig.~4 are the
  same.}
\label{fig:mirror}
\end{center}
\end{figure}
